\begin{acknowledgements}
    To begin, I would like to thank Dr Mohammadali Foroozandeh, my primary
    supervisor for the majority of my PhD. It was an honour to be able to
    discuss my work with him; his deep insights into a plethora of
    topics in magnetic resonance is inspiring if a little daunting to
    mortals like myself.
    %%% Struggling with wording of this
    % His style of supervision was very beneficial for me, allowing me to pursue
    % interests beyond my PhD work, even though it could be argued that I spent
    % too much time learning about the Vim text editor and the Rust programming
    % language.
    His passion for literature and music also rubbed off on me; while they
    frequently had a rather violent bent\,---\,Cormac McCarthy's \emph{Blood
    Meridian} and an opera by Alfred Schnittke on Faust come to mind\,---\,I
    cannot say that his recommendations were ever dull.
    It was a pleasure to be part of the Foroozandeh group; thanks to fellow
    members Jonanthan Yong, Jean-Baptiste Verstraete, Ali Sherzad, David
    Goodwin, Thomas Moss, and Daniel Alimadadian for the numerous discussions
    and pints over the years.
    For their generosity in covering my course fees and living costs, I'd like
    to thank \textsc{The Royal Society}, the funders of Dr Foroozandeh's research
    stipend.

    Prof. Timothy Claridge acted as my co-supervisor alongside Dr Foroozandeh.
    The regular meetings on NMR that he hosted in the Chemistry Department were
    very valuable, with them both informing me on how people were
    applying NMR in their research, and giving me countless opportunities to
    present my work and other topics of interest.

    Both Dr Foroozandeh and Prof. Claridge left the department during my PhD;
    % Dr Foroozandeh now works on quantum computing at \textsc{Zurich
    % Instruments}, while Prof. Claridge is the director of a new NMR facility at
    % \textsc{Exscientia}.
    I wish them both the best with their new endeavours.
    I am very grateful to Dr Fay Probert for taking over my supervision for the
    latter stages of my PhD, providing valuable advice and assistance.
    I'd like to thank her and the rest of her group for being so welcoming to
    me during the last year of my PhD. I'd also like to acknowledge Dr James
    Montgomery, who was kind enough to support me with the
    operation of the department's NMR spectrometers when I eventually decided
    I should acquire some of my own data.

    During my 8 years both as an undergraduate and postgraduate student at
    Oxford, I met many wonderful people that made my time thoroughly enjoyable.
    To name a few, thanks to the 2015 Jesus College Chemists, Eve, Lauren,
    Ryan, Joe H, Caitlin, Jenyth, Dominic, Linda, Daniel, Valeria, Joe L, Nick,
    and James.  Most of all, I am immeasurably grateful to Isobel, for her
    support and inspiration throughout my Masters and PhD; I truly could not
    have done it without her encouragement. Thanks too to Laura,
    Katherine, and of course Pixie, for hosting me numerous times in the
    Cotswolds.

    Finally, to my family\,---\,Mum, Dad, and (most of the time)
    Robert\,---\,your enduring love and support cannot be understated.
\end{acknowledgements}
