\chapter{Pure shift spectra from 2D J-resolved estimation}

Two key features of the \ac{NMR} experiment for which improvements are
constantly being sought are sensitivity and resolving power. There are numerous
means of enhancing sensitivity, including technological advancements such as
production of superconducting magnets with higher field
strengths\cite{Maeda2019} (sensitivity $\propto B_0^{\nicefrac{7}{4}}$) and
cryogenic probes\cite{Styles1984,Styles1989,Kovacs2005}, as well as simply
increasing the number of scans (sensitivity $\propto \sqrt{\text{no. scans}}$).
However, few means of achieving better resolution exist beyond increased field
strengths (resolution $\propto B_0$). \note{Perhaps mention improved field
homogeneities (shimming)?} Significant interest has therefore been given to the
development of techniques which generate broadband homodecoupled (\emph{pure
shift}) spectra, in which the effects of homonuclear scalar couplings are
absent from the data. While often valuable for structural assignment purposes,
the influence of scalar couplings can lead to spectra which are too crowded for
meaningful insights to be gleamed. While it is commonplace to decouple
heteronuclear couplings at the point of \ac{FID} acquisition\cite{Shaka1983a,
Shaka1983b,Shaka1985}, homonuclear decoupling is far more challenging. At
the time of writing, there are a number of of well-established pure shift
experiments, which involve running a \ac{2D} pulse sequence, and concatenating
the initial section of each \ac{FID}, in a process referred to as
chunking\cite{Meyer2013,Adams2014,Zangger2015}. The key drawback of all of
these techniques is that the resultant pure shift signal is considerably less sensitive relative to a standard pulse-acquire experiment, since only a subset
\note{Does ``subset'' make sense?} of the available spin magnetisation
contributes that which is detectable.
\note{Describe strong couplings if this has not been done before now}.

In this chapter, after a survey of the key pure shift techniques, a method for
deriving pure shift spectra indirectly via the estimation of \ac{2DJ} datasets
is presented, which has been given the name \acf{CUPID}. It is illustrated that
by extracting the parameters which describe a \ac{2DJ} dataset, a pure shift
spectrum can be produced without the signal loss associated with all
experimental pure shift methods, and with desirable absorption-mode lineshapes.

\input{text/main/4_cupid_1_pure_shift}
\input{text/main/4_cupid_2_methodology}
\input{text/main/4_cupid_3_results}
\input{text/main/4_cupid_4_summary}
